Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-24 paper/paper.tex
pass on results
pass on javascript section

Both the specification and implementation of JavaScript are
incomplete. Certain parts of the specification are undefined; it is
responsibility of engine engineers to decide how to implement these
functionalities. The JavaScript spec uses the label
``implementation-dependent'' to indicate these cases, where behavior
may differ from engine to engine. One reason this flexibility in the
spec exists is to enable compiler optimizations. For example, the
\mcodeid{for-in} loop does not clearly specify the iteration
order~\cite{so-forin-undefined,javascript-in-chrome} and different
engines capitalize on that~\cite{for-in-undefined}.  As another
example, the latest version of the \es{} specification states that if
the \mcodeid{Number.toPrecision()} function is called with more than
one argument, then the behavior is
implementation-dependent~\cite{es6-toPrecision}. Various other cases
like these exist in the specification. Such gap also exists at the
implementation level. Given the speed the specification changes and
the complexity of the language some features are not fully implemented
as can be observed by the Kangax compatibility table~\cite{kangax}.

\sloppy It is also worth noting that, as in other languages, some
elements in JS have non-deterministic behavior (\eg{},
\mcodeid{Math.random} and \mcodeid{Date}). A test that make decisions
based on these elements could, in principle, produce different
outcomes on different runs. Carefully-written test cases should not
manifest this kind of
flakiness~\cite{luo-etal-fse2014,palomba-zaidman-icsme2017}, but
fuzzed test files could are more likely, intuitively, to manifest
them.

As mentioned previously, all those aspects make testing \js\ engines
more challenging.

>>>>

The specification and implementation of JavaScript are
incomplete. Certain parts of the specification are undefined; it is
responsibility of engine engineers to decide how to implement these
functionalities. The JavaScript spec uses the label
``implementation-dependent'' to indicate these cases, where behavior
may differ from engine to engine. One reason this flexibility in the
spec exists is to enable compiler optimizations. For example, the
\mcodeid{for-in} loop does not clearly specify the iteration
order of elements~\cite{so-forin-undefined,javascript-in-chrome} and different
engines capitalize on that for optimization~\cite{for-in-undefined}.  As another
example, the specification states that if
the \mcodeid{Number.toPrecision()} function is called with multiple arguments then the floating-point approximation is
implementation-dependent~\cite{es6-toPrecision}. Various other cases
like these exist in the specification. Such gap also exists at the
implementation level. Given the speed the specification changes and
the complexity of the language some features are not fully implemented
as can be observed by the Kangax compatibility table~\cite{kangax}.
It is also worth noting that, as in other languages, some
elements in JS have non-deterministic behavior (\eg{},
\mcodeid{Math.random} and \mcodeid{Date}). A test that make decisions
based on these elements could, in principle, produce different
outcomes on different runs. Carefully-written test cases should not
manifest this kind of
flaky behavior~\cite{luo-etal-fse2014,palomba-zaidman-icsme2017}, but
fuzzed are more likely to manifest them.
As mentioned previously, all those aspects make testing \js\ engines
more challenging.
